Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-03-21 doc/PRF2022/PRF_main.tex
read up to start of Sec V

\begin{abstract}
  Active colloidal systems with non-equilibrium self-organization is a
  long-standing, challenging area in material sciences and biology. To understand how
  hydrodynamic flow may be used to actively control self-assembly of
  Janus particles (JPs), we developed  a model for the
  many-body hydrodynamics of amphiphilic JPs suspended in a viscous
  fluid with imposed far-field background flows (Journal of Fluid Mech., 941, 2022). 
  In this work we alter the hydrophobic distribution on the JP-solvent
  interface to investigate the hydrodynamics that underlies the various
  morphologies and rheological properties of the JP assembly in the
  suspension.
  We find JPs assemble into uni-lamella,
  multi-lamella, and striated structures. To introduce dynamics, we
  include a planar linear shear flow and a steady Taylor-Green mixing flow, and
  measure the collective dynamics of JP particles in terms of their (a)
  free energy from the hydrophobic interactions between the JPs, (b)
  order parameter for the ordering of JPs in terms of alignment of their
  directors, and (c) strain parameter that captures the deformation in
  the assembly. We characterize the effective material properties of the
  JP structures and find that the uni-lamellar structures increases
  orientation order under shear flow, the multilamellar structure
  behaves as a shear thinning fluid, and the striated structure
  possesses a yield stress. These numerical results provide insights
  into dynamic control of non-equilibrium active biological systems with
  similar self-organization.
\end{abstract}

@@

\section{Introduction}
% Put \label in argument of \section for cross-referencing
%\section{\label{}}
Janus particles are colloids with dissimilar chemical or
physical functionalities between the two sides of their surfaces
~\cite{deGennes1992,KirillovaMarschelkeSynytska2019}. Self-propelling Janus
particles, for example, with a permanent biphasic asymmetry, have
emerged as a rich chemical platform for the exploration of active
matter~\cite{Meredithetal2022} and mobility induced phase separation.
In the absence of mobility and any
imposed flow, Janus particles (JPs) self-assemble
into oligomers of various geometries
and sizes
depending on the interactions between JPs and the 
viscous solvent~\cite{Bradley2017, KangHonciuc2018,
HongCacciutoLuijtenGranick2008},
with tunable functions for biomedical engineering
applications~\cite{GheisariSahfieeAbbasiEtAl2021_DMR,
LiuYangHuangEtAl2016_Angew, LiWangYaoEtAl2019_Nanoscale,
Bradley2016,Zarzaretal2015, KirillovaMarschelkeSynytska2019}.

When driven by an external flow, dynamic rearrangement of JPs emerges
naturally from the interactions between particles and fluid in colloidal
matter~\cite{RevModPhys.93.025008}. Such colloidal hydrodynamics
belong to a wide class of nonequilibrium self-organization in physics,
often with complexity and features similar to that of biological systems
such as living cells, bacterial baths, and animal
flocks~\cite{CollardGrosjeanVandewalle2020, Vutukuri2020}. A
long-standing challenge in fluid mechanics and material science is to
solve the ``inverse" problem of creating a model colloidal system that
will self-assemble into prescribed
structures~\cite{PhysRevLett.128.256102}. For example, the framework of
geometrical frustration, which has been used to explain disordered
systems, could instead be used to design new, ordered systems, through
specific choices for the shapes or interactions of the
particles~\cite{Manoharan2015_Science}.

In this work we focus on collective hydrodynamics of immobile
amphiphilic JPs in a
viscous fluid under an imposed far-field flow. The amphiphilic JP has a
hydrophobic surface on one side and a hydrophilic surface on the other
side \cite{doi:10.1021/la503455h}.
The many-body hydrodynamics of amphiphilic Janus particles assembled as
vesicles (self-enclosed bilayers of JPs) suspended in a viscous fluid in the inertialess regime (zero
Reynolds number) has been studied using boundary integral numerical
simulations~\cite{Fu20,Fu2022_JFM}. The dynamics of the JP suspension
results from the combination of long-range hydrodynamic interaction and
non-local interactions between JPs through the distribution of a
hydrophobic attraction potential (HAP).
%
In a quiescent flow, a JP suspension 
self-assemble into micelles and bilayers of JPs that provide an
alternative means for computing the mechanical moduli of a colloidal
membrane in numerical simulations~\cite{NaTr00, Fu20, KrFiGuKaHa13}. Under background flows, the
hydrodynamics of a JP vesicle (a self-enclosed bilayer of JPs) exhibit
many familiar behaviors of a vesicle: elongation and alignment along the
extensional direction, tank-treading, and rupture of a vesicle under
shear flow~\cite{Fu2022_JFM, grandmaison_brancherie_salsac_2021,
D2SM00179A,keller_skalak_1982, Finken08, Shaqfeh11}.

@@

This paper is organized as follows. \S~II summarizes the general
mathematical formulation. \S~III describes the three types of
hydrophobicity distribution that we use in the numerical simulations.
\S~IV outlines the quantitative measures used to describe the collective
hydrodynamics of JPs summarized and discussed in \S~V. \S~VI provides a
conclusion and discussion for future directions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Governing Equations: Hydrophobic Attraction Potential Mobility Problem} 
The governing equations are a system for the position and
orientation of a collection of rigid JPs~\cite{Fu2022_JFM}.
We first pose the
Stokes equations for the mobility problem giving the hydrodynamic
interactions for the particle suspension. The hydrophobic forces come
from solving a screened Laplace equation. Particle collisions are
avoided through a near-field, pair potential.

@@

To obtain forces, define the free
energy~\cite{Fu20, Fu2022_JFM}
\begin{align}
\label{eq:free_energy}
F = \gamma
  \int_{\Omega} \left(\rho |\nabla u|^2 + \rho^{-1} u^2 \right)
\,d\xx
+ \frac{M}{2}
\sum_{j \neq i} 
P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right),
\end{align}
where $u(\xx,t)$ is as the order parameter for water\cite{Ma77, GoHaKo94},
$\rho$ is a decay length, and $\gamma$ is an interfacial tension. 
The order parameter $u(\xx,t)$ is assumed to minimize the free energy
$F$ and therefore satisfies the screened Laplace boundary value problem
\begin{gather}
  \label{eq:SL}
  -\rho^2 \Delta u + u = 0,\quad \xx \in \Omega, \\
  \label{eq:SLbc}
  u = g, \quad \xx \in \bd\Omega, \quad 
  u \rightarrow 0, \quad |\xx| \rightarrow \infty.
\end{gather}
The boundary condition $g$ encodes hydrophobic properties of the
particle-solvent interface.
The dimensionless repulsion profile $P$ takes the form $P(s) = 1 -
\sin(\pi s/2)$ for $0 \leq s < 1$ and $P(s) = 0$ for
$s \geq 1$. The parameter $\rho_0$ is the distance 
below which steric repulsion becomes important and 
$M$ is the repulsion modulus.

@@

For the velocity, we use the completed double-layer potential
representation~\cite{pow-mir1987}
\begin{align}
  \label{eq:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DDD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \cdot \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega,
\end{align}
where $\eeta$ is a vector-valued density function and
\begin{align}
  \DDD[\eeta](\xx) = \frac{1}{\pi} \int_{\Gamma} 
    \frac{(\xx - \yy) \cdot \nnu_\yy}{|\xx - \yy|^2}
    \frac{(\xx - \yy) \otimes (\xx - \yy)}{|\xx - \yy|^2}
    \cdot \eeta(\yy)\, \dif s_\yy.
\end{align}
The Stokeslets and Rotlets are
\begin{align}
  \SS(\xx,\aa_i) = \frac{1}{4\pi} \left(-\log |\rr|\mathbf{I} +
    \frac{\rr \otimes \rr}{|\rr|^2}\right), \quad 
  \RR(\xx,\aa_i) = \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2}, 
\end{align}
respectively, where $\rr = \xx - \aa_i$. Letting
$\xx$ approach $\Gamma_i$ in~\eqref{eq:velocity}, applying the jump
condition of the double layer potential~\cite{poz1992}, and imposing the
no-slip boundary condition~\eqref{eq:rigid-vel}, the density function
$\eeta$, translational velocity $\vv_i$, and rotational velocity
$\omega_i$ satisfy
\begin{alignat}{3}
  \label{eq:vel_BLM_rep}
  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
    -\frac{1}{2} \eeta(\xx) + \DDD[\eeta](\xx) 
    + \sum_{j=1}^{N_b} 
    \left(\SS(\xx,\aa_j) \cdot \FF_j + \RR(\xx,\aa_j) T_j\right),\\
  \label{eq:vel_BLM_rep2}
  \int_{\Gamma_i} \eeta \, \dif s &= \mathbf{F}_i, \quad
  \int_{\Gamma_i} \eeta \cdot (\xx-\aa_i)^\perp \, \dif s = T_i,
\end{alignat}
for $\xx \in \Gamma_i$ and $i = 1,\ldots,N_b$.
%Equation~\eqref{eq:vel_BLM_rep}--\eqref{eq:vel_BLM_rep2} does have a
%unique solution, but we note that
Alternative full-rank layer potential
representations for rigid body motions are possible~\cite{rac-gre2016,
cor-gre-rac-vee2017}.

@@

After discretizing and applying quadrature, the result is an $NN_b
\times NN_b$ and $(2N+3)N_b \times (2N+3)N_b$ linear system
for~\eqref{eq:SL_BIE2}
and~\eqref{eq:vel_BLM_rep}--\eqref{eq:vel_BLM_rep2}, respectively.
These are solved with matrix-free GMRES and the second-kind BIEs
guarantee that the number of GMRES iterations is mesh-independent.

@@

\section{Tunable hydrophobicity}
\label{sec:tunable_hydrophobicity}
The parameters are modeled after those for
phospholipid in water~\cite{Boal}.
We use $\mu = 1$~mPa~s for the viscosity of water
at room temperature. Pure lipid components give a range of interfacial
tensions~\cite{KUZMIN2005, Petelska2012,Jackson2016, GarciaSaez}; $0.7$--$5.3$~pN~nm$^{-1}$.
We use $\gamma=4.1$~pN~nm$^{-1}$ which gives a physically reasonable 
elastic modulus $\kappa$ of lipid bilayers~\cite{Fu20,Fu2022_JFM}.
The particle radius $c = 1.25$~nm represents one half 
of phospholipid length~\cite{Boal}, and the screening length $\rho = 5$~nm
derives from experimental force-distance measurements of hydrophobic
attraction~\cite{ErLjCl89,Lietal05,Israelachvili80,Jackson2016}. 
A repulsion modulus $M = 2$~pN and 
distance $\rho_0 = 0.5$~nm gives an interparticle distance around one
particle radius, ensuring the accuracy of the boundary integral
representations~\eqref{eq:SL_BIE} and~\eqref{eq:velocity} without 
overly aggressive mesh refinement. The characteristic time
and length are $1$~ns and  $1$~nm, respectively.

\begin{figure}[t!]
\begin{center}
  \includegraphics[width=\textwidth]{Figures/Figure0.pdf}
\end{center}
\begin{caption}{\label{fig:boundary_conditions} The leftmost diagram
  illustrates the particle $\Gamma_i$ with center $\aa_i$, radius $c$,
  and director $\dd$, along with the angle $\alpha$.
  The three rightmost panels plots show $g(\xx)$ and
  the respective solutions $u(\xx)$ of~\eqref{eq:SL} 
  for an isolated particle.}
\end{caption}
\end{figure}
\subsection{Boundary conditions and equilibrium configurations}
The boundary condition $g(\xx)$ in
\eqref{eq:SLbc} defines the spatial distribution of
hydrophobicity and hydrophilicity.
Referring to Figure \ref{fig:boundary_conditions},
\begin{align}
  \label{eq:bc-type}
g(\xx) = a(b + \cos \alpha),\quad a = (\pi c(2b^2 + 1))^{-1/2},\quad \xx \in \Gamma_i,
\end{align}
where $\alpha$ is the angle between the vector $\xx - \aa_i$ and the
particle director $\dd_i = (\cos \theta_i, \sin \theta_i)$
The scalar $b$ shifts the periodic date up and down and the scalar
$a$ normalizes $g$ so that $\int_{\Gamma_i} g^2(\xx) \, \dif s = 1$.
The side of the particle where
$\alpha = 0$ is called the tail and the side where $\alpha = \pi$ is the head.

@@

For Type II, asymmetric hydrophobes,
both sides of the JP are hydrophobic but more so on the tail.
Over short times, these particles self-assemble into bilayers. But unlike for
Type I JPs, the heads are also hydrophobic and so over long times, 
the bilayers sort into a ``multilamellar'' phase.
The number of layers depends on the number of particles.
Figure~\ref{fig:relax}(c), for example, shows a multilamellar structure
with four layers and one with two layers in the inset.
Onion-like dendrimersomes have previously been studied by molecular dynamics
simulations using an 
anisotropic pair potential~\cite{C9NR05885K,HongCacciutoLuijtenGranick2008}.

Finally, Type III, bipolar JPs possess a
head that repels the tail of neighboring particles.
These JP initially form chains with
their directors perpendicular to the length of the chain. The chains
form stria where the particles lie on a square grid and the orientations
alternate between layers (Figure~\ref{fig:relax}(d)).
We refer to this as the ``striated'' phase.

@@

\section{Measuring deformation}
To quantify the hydrodynamics of JP phases,
we use the free energy $F$, a strain parameter $E$, and
a scalar order parameters $S_{2}$ for alignment.
First we simplify the form of the free energy~\eqref{eq:free_energy}.
Using integration by parts and~\eqref{eq:SL}, we obtain
\begin{equation}
\label{eq:free_energy2}
F = -\gamma
\int_{\partial \Omega} \rho g \nabla u \cdot \nnu \,\dif s
+ \frac{M}{2}
\sum_{j \neq i} 
P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right).
\end{equation}
%
Here, we have substituted $g$ for $u$ since the boundary values are
given. However, evaluating $\nabla u \cdot \nnu$ on $\partial \Omega$ based
on~\eqref{eq:SL_BIE} involves calculating a quadruple layer potential
which has a well-known obstacle in numerical implementation.
Appendix \S\ref{sec:appendix} describes
how we overcome this obstacle.

@@

Finally, we use the scalar order parameter $S_2$
to quantify the orientational order\cite{Selinger2016}:
\begin{equation}
  \label{eq:S2}
S_2 = \frac{1}{N_b} \sum_{i=1}^{N_b} \frac{1}{2}(3\cos^2(\theta_i - \bar \theta) - 1).
\end{equation}
Here $\bar \theta_i$ is a circular mean defined as the orientation of the
principal eigenvector of the matrix
$\sum_{j} \dd_j\dd_j^\top$ where $j$ runs over the particles
whose centers lie with $4c$ of that of particle $i$. 
Defined as such, $S_2$ lies in the range $-1/2 \le S_2 \le 1$
with a value $S_2 = 1$ indicating perfect alignment between particles
while $S_2=-1/2$ indicating isotropic alignment locally.
The cutoff distance $4c$ was chosen empirically
so that the average includes nearest neighbors
but excludes next nearest neighbors.

@@

The striated phase order admits more than one pattern
depending on the number of particles (Figure~\ref{fig:relax}(f), triangles).
When the number of particles is fewer, there is only a
single pattern where the directors are more or
less parallel and alternate directions (Figure~\ref{fig:relax}(e),
inset). Larger number of particles results in multiple alignment patterns:
the alternating sign pattern as in the small particle number case
(Figure~\ref{fig:relax}(e), top right rectangle) and an 'X'-shaped
alignment (Figure~\ref{fig:relax}(e), top left rectangle).

>>>>

\begin{abstract}
  Active colloidal systems with non-equilibrium self-organization is a
  long-standing, challenging area in material sciences and biology. To
  understand how hydrodynamic flow may be used to actively control
  self-assembly of Janus particles (JPs), we developed a model for the
  many-body hydrodynamics of amphiphilic JPs suspended in a viscous
  fluid with imposed far-field background flows (Journal of Fluid
  Mechanics, 941, 2022). In this work we alter the hydrophobic
  distribution on the JP-solvent interface to investigate the
  hydrodynamics that underlies the various morphologies and rheological
  properties of the JP assembly in the suspension. We find JPs assemble
  into uni-lamella, multi-lamella, and striated structures. To introduce
  dynamics, we include a planar linear shear flow and a steady
  Taylor-Green mixing flow, and measure the collective dynamics of JP
  particles in terms of their (a) free energy from the hydrophobic
  interactions between the JPs, (b) order parameter for the ordering of
  JPs in terms of alignment of their directors, and (c) strain parameter
  that captures the deformation in the assembly. We characterize the
  effective material properties of the JP structures and find that the
  uni-lamellar structures increases orientation order under shear flow,
  the multilamellar structure behaves as a shear thinning fluid, and the
  striated structure possesses a yield stress. These numerical results
  provide insights into dynamic control of non-equilibrium active
  biological systems with similar self-organization.
\end{abstract}

@@

\section{Introduction}
% Put \label in argument of \section for cross-referencing
%\section{\label{}}
Janus particles (JPs) are colloids with dissimilar chemical or physical
functionalities between the two sides of their surfaces
~\cite{deGennes1992,KirillovaMarschelkeSynytska2019}. Self-propelling
JPs, for example, with a permanent biphasic asymmetry, have emerged as a
rich chemical platform for the exploration of active
matter~\cite{Meredithetal2022} and mobility induced phase separation.
In the absence of mobility and any imposed flow, JPs self-assemble into
oligomers of various geometries and sizes depending on the interactions
between JPs and the viscous solvent~\cite{Bradley2017, KangHonciuc2018,
HongCacciutoLuijtenGranick2008}, with tunable functions for biomedical
engineering applications~\cite{GheisariSahfieeAbbasiEtAl2021_DMR,
LiuYangHuangEtAl2016_Angew, LiWangYaoEtAl2019_Nanoscale,
Bradley2016,Zarzaretal2015, KirillovaMarschelkeSynytska2019}.

When driven by an external flow, dynamic rearrangement of JPs emerges
naturally from the interactions between particles and fluid in colloidal
matter~\cite{RevModPhys.93.025008}. Such colloidal hydrodynamics
belong to a wide class of nonequilibrium self-organization in physics,
often with complexity and features similar to that of biological systems
such as living cells, bacterial baths, and animal
flocks~\cite{CollardGrosjeanVandewalle2020, Vutukuri2020}. A
long-standing challenge in fluid mechanics and material science is to
solve the ``inverse'' problem of creating a model colloidal system that
will self-assemble into prescribed
structures~\cite{PhysRevLett.128.256102}. For example, the framework of
geometrical frustration, which has been used to explain disordered
systems, could instead be used to design new, ordered systems, through
specific choices for the shapes or interactions of the
particles~\cite{Manoharan2015_Science}.

In this work we focus on collective hydrodynamics of immobile
amphiphilic JPs in a
viscous fluid under an imposed far-field flow. The amphiphilic JP has a
hydrophobic surface on one side and a hydrophilic surface on the other
side \cite{doi:10.1021/la503455h}.
The many-body hydrodynamics of amphiphilic Janus particles assembled as
vesicles (self-enclosed bilayers of JPs) suspended in a viscous fluid in the inertialess regime (zero
Reynolds number) has been studied using boundary integral numerical
simulations~\cite{Fu20,Fu2022_JFM}. The dynamics of the JP suspension
results from the combination of long-range hydrodynamic interaction and
non-local interactions between JPs through the distribution of a
hydrophobic attraction potential (HAP).
%
In a quiescent flow, a JP suspension self-assembles into micelles and
bilayers of JPs that provide an alternative means for computing the
mechanical moduli of a colloidal membrane in numerical
simulations~\cite{NaTr00, Fu20, KrFiGuKaHa13}. Under background flows,
the hydrodynamics of a JP vesicle (a self-enclosed bilayer of JPs)
exhibit many familiar behaviors of a vesicle: elongation and alignment
along the extensional direction, tank-treading, and rupture of a vesicle
under shear flow~\cite{Fu2022_JFM, grandmaison_brancherie_salsac_2021,
D2SM00179A,keller_skalak_1982, Finken08, Shaqfeh11}.

@@

This paper is organized as follows. \S~\ref{sec:governing_equations}
summarizes the general mathematical formulation.
\S~\ref{sec:tunable_hydrophobicity} describes the three types of
hydrophobicity distribution that we use in the numerical simulations.
\S~\ref{sec:measuring_deformation} outlines the quantitative measures
used to describe the collective hydrodynamics of JPs summarized and
discussed in \S~\ref{sec:results}. Finally, \S~\ref{sec:conclusion}
provides a conclusion and discussion for future directions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Governing Equations: Hydrophobic Attraction Potential Mobility Problem} 
\label{sec:governing_equations}
The governing equations are a system for the position and orientation of
a collection of rigid JPs~\cite{Fu2022_JFM}. We first pose the Stokes
equations for the mobility problem giving the hydrodynamic interactions
for the particle suspension. The hydrophobic forces come from solving a
screened Laplace equation. Particle collisions are avoided through a
near-field, pair potential.

@@

To obtain forces, define the free
energy~\cite{Fu20, Fu2022_JFM}
\begin{align}
\label{eq:free_energy}
F = \gamma
  \int_{\Omega} \left(\rho |\nabla u|^2 + \rho^{-1} u^2 \right)
\,d\xx
+ \frac{M}{2}
\sum_{j \neq i} 
P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right),
\end{align}
where $u(\xx,t)$ is as the order parameter for water~\cite{Ma77,
GoHaKo94}, $\rho$ is a decay length, and $\gamma$ is an interfacial
tension. The order parameter $u(\xx,t)$ is assumed to minimize the free
energy $F$ and therefore satisfies the screened Laplace boundary value
problem
\begin{gather}
  \label{eq:SL}
  -\rho^2 \Delta u + u = 0,\quad \xx \in \Omega, \\
  \label{eq:SLbc}
  u = g, \quad \xx \in \bd\Omega, \quad 
  u \rightarrow 0, \quad |\xx| \rightarrow \infty.
\end{gather}
The boundary condition $g$ encodes hydrophobic properties of the
particle-solvent interface.  The dimensionless repulsion profile takes
the form $P(s) = 1 - \sin(\pi s/2)$ for $0 \leq s < 1$ and $P(s) = 0$
for $s \geq 1$. The parameter $\rho_0$ is the distance below which
steric repulsion becomes important and $M$ is the repulsion modulus.

@@

For the velocity, we use the completed double-layer potential
representation~\cite{pow-mir1987}
\begin{align}
  \label{eq:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DDD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \cdot \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega,
\end{align}
where $\eeta$ is a vector-valued density function and
\begin{align}
  \DDD[\eeta](\xx) = \frac{1}{\pi} \int_{\Gamma} 
    \frac{(\xx - \yy) \cdot \nnu_\yy}{|\xx - \yy|^2}
    \frac{(\xx - \yy) \otimes (\xx - \yy)}{|\xx - \yy|^2}
    \cdot \eeta(\yy)\, \dif s_\yy.
\end{align}
The Stokeslets and Rotlets are
\begin{align}
  \SS(\xx,\aa_i) = \frac{1}{4\pi} \left(-\log |\rr|\mathbf{I} +
    \frac{\rr \otimes \rr}{|\rr|^2}\right), \quad 
  \RR(\xx,\aa_i) = \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2}, 
\end{align}
respectively, where $\rr = \xx - \aa_i$. Letting
$\xx$ approach $\Gamma_i$ in~\eqref{eq:velocity}, applying the jump
condition of the double layer potential~\cite{poz1992}, and imposing the
no-slip boundary condition~\eqref{eq:rigid-vel}, the density function
$\eeta$, translational velocity $\vv_i$, and rotational velocity
$\omega_i$ satisfy
\begin{alignat}{3}
  \label{eq:vel_BLM_rep}
  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
    -\frac{1}{2} \eeta(\xx) + \DDD[\eeta](\xx) 
    + \sum_{j=1}^{N_b} 
    \left(\SS(\xx,\aa_j) \cdot \FF_j + \RR(\xx,\aa_j) T_j\right),\\
  \label{eq:vel_BLM_rep2}
  \int_{\Gamma_i} \eeta \, \dif s &= \mathbf{F}_i, \quad
  \int_{\Gamma_i} \eeta \cdot (\xx-\aa_i)^\perp \, \dif s = T_i,
\end{alignat}
for $\xx \in \Gamma_i$ and $i = 1,\ldots,N_b$. Alternative full-rank
layer potential representations for rigid body motions are
possible~\cite{rac-gre2016, cor-gre-rac-vee2017}.

@@

After discretizing and applying quadrature, the result is an $NN_b
\times NN_b$ and $(2N+3)N_b \times (2N+3)N_b$ linear system
for~\eqref{eq:SL_BIE2}
and~\eqref{eq:vel_BLM_rep}--\eqref{eq:vel_BLM_rep2}, respectively.
These are solved with matrix-free GMRES and the second-kind nature of
the BIEs guarantees that the number of GMRES iterations is
mesh-independent.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Tunable hydrophobicity}
\label{sec:tunable_hydrophobicity}
The parameters are modeled after those for phospholipid in
water~\cite{Boal}. We use $\mu = 1$~mPa~s for the viscosity of water at
room temperature. Pure lipid components give a range of interfacial
tensions~\cite{KUZMIN2005, Petelska2012,Jackson2016, GarciaSaez};
$0.7$--$5.3$~pN~nm$^{-1}$. We use $\gamma=4.1$~pN~nm$^{-1}$ which gives
a physically reasonable elastic modulus $\kappa$ of lipid
bilayers~\cite{Fu20, Fu2022_JFM}. The particle radius $c = 1.25$~nm
represents one half of phospholipid length~\cite{Boal}, and the
screening length $\rho = 5$~nm derives from experimental force-distance
measurements of hydrophobic attraction~\cite{ErLjCl89, Lietal05,
Israelachvili80, Jackson2016}. A repulsion modulus $M = 2$~pN and
distance $\rho_0 = 0.5$~nm gives an interparticle distance around one
particle radius, ensuring the accuracy of the boundary integral
representations~\eqref{eq:SL_BIE} and~\eqref{eq:velocity} without overly
aggressive mesh refinement. The characteristic time and length are
$1$~ns and $1$~nm, respectively.

\begin{figure}[t!]
\begin{center}
  \includegraphics[width=\textwidth]{Figures/Figure0.pdf}
\end{center}
\begin{caption}{\label{fig:boundary_conditions} The leftmost diagram
  illustrates the particle $\Gamma_i$ with center $\aa_i$, radius $c$,
  and director $\dd$, along with the angle $\alpha$.
  The three rightmost panels plots show $g(\xx)$ and
  the respective solutions $u(\xx)$ of~\eqref{eq:SL} 
  for an isolated particle.}
\end{caption}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundary conditions and equilibrium configurations}
The boundary condition $g(\xx)$ in \eqref{eq:SLbc} defines the spatial
distribution of hydrophobicity and hydrophilicity.  Referring to Figure
\ref{fig:boundary_conditions}, we let
\begin{align}
  \label{eq:bc-type}
g(\xx) = a(b + \cos \alpha),\quad a = (\pi c(2b^2 + 1))^{-1/2},\quad \xx \in \Gamma_i,
\end{align}
where $\alpha$ is the angle between the vector $\xx - \aa_i$ and the
particle director $\dd_i = (\cos \theta_i, \sin \theta_i)$.  The scalar
$b$ shifts the periodic date up and down and the scalar $a$ normalizes
$g$ so that $\int_{\Gamma_i} g^2(\xx) \, \dif s = 1$. The side of the
particle where $\alpha = 0$ is called the tail and the side where
$\alpha = \pi$ is the head.

@@

For Type II, asymmetric hydrophobes, both sides of the JP are
hydrophobic but more so on the tail. Over short times, these particles
self-assemble into bilayers. But unlike for Type I JPs, the heads are
also hydrophobic and so over long times, the bilayers sort into a
``multilamellar'' phase. The number of layers depends on the number of
particles. Figure~\ref{fig:relax}(d), for example, shows a multilamellar
structure with four layers and one with two layers in the inset.
Onion-like dendrimersomes have previously been studied by molecular
dynamics simulations using an anisotropic pair
potential~\cite{C9NR05885K,HongCacciutoLuijtenGranick2008}.

Finally, Type III, bipolar JPs possess a head that repels the tail of
neighboring particles. These JP initially form chains with their
directors perpendicular to the length of the chain. The chains form
stria where the particles lie on a square grid and the orientations
alternate between layers (Figure~\ref{fig:relax}(e)). We refer to this
as the ``striated'' phase.

@@

\section{Measuring deformation}
\label{sec:measuring_deformation}
To quantify the hydrodynamics of JP phases, we use the free energy $F$,
a strain parameter $E$, and a scalar order parameters $S_{2}$ for
alignment. First we simplify the form of the free
energy~\eqref{eq:free_energy}. Using integration by parts
and~\eqref{eq:SL}, we obtain
\begin{equation}
\label{eq:free_energy2}
F = -\gamma
\int_{\partial \Omega} \rho g \nabla u \cdot \nnu \,\dif s
+ \frac{M}{2}
\sum_{j \neq i} 
P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right).
\end{equation}
%
Here, we have substituted $g$ for $u$ since the boundary values are
given. However, evaluating $\nabla u \cdot \nnu$ on $\partial \Omega$
based on~\eqref{eq:SL_BIE} involves calculating a gradient of a
double-layer potential which has a well-known obstacle in numerical
implementation. Appendix~\ref{sec:appendix} describes how we overcome
this obstacle.

@@

Finally, we use the scalar order parameter $S_2$ to quantify the
orientational order~\cite{Selinger2016}:
\begin{equation}
  \label{eq:S2}
S_2 = \frac{1}{N_b} \sum_{i=1}^{N_b} \frac{1}{2}(3\cos^2(\theta_i - \bar \theta) - 1).
\end{equation}
Here $\bar \theta_i$ is a circular mean defined as the orientation of
the principal eigenvector of the matrix $\sum_{j} \dd_j\dd_j^\top$ where
$j$ runs over the particles whose centers lie with $4c$ of that of
particle $i$.  Defined as such, $S_2$ lies in the range $-1/2 \le S_2
\le 1$ with a value $S_2 = 1$ indicating perfect alignment between
particles while $S_2=-1/2$ indicating isotropic alignment locally.  The
cutoff distance $4c$ was chosen empirically so that the average includes
nearest neighbors but excludes next nearest neighbors.

@@

The striated phase order admits more than one pattern depending on the
number of particles (Figure~\ref{fig:relax}(f), triangles).  When the
number of particles is fewer, there is only a single pattern where the
directors are more or less parallel and alternate directions
(Figure~\ref{fig:relax}(e), inset). Larger number of particles results
in multiple alignment patterns: the alternating sign pattern as in the
small particle number case (Figure~\ref{fig:relax}(e), top right
rectangle) and an `X'-shaped alignment (Figure~\ref{fig:relax}(e), top
left rectangle).
